### 2018-06-21 Sections/optimising_the_world.tex
Irrelevance of latency, traffic opt fig update
Upgrade texlive2018

\begin{figure}[!htb]
	\includegraphics[width=0.4\textwidth]{traffic_optimisation}
	\caption{Simple road network, where vertices represent intersections and edges represent roads. Edge weights indicate their associated travel time. The goal is for Alice and Bob to both drive home optimally, i.e minimising net commute time. Let us assume that the intersections do not delay single cars, but if they become congested (i.e more than one car simultaneously) they induce a time delay of 1 on all drivers present at the intersection. If Bob were to stay at work, and only Alice was attempting to drive home, her optimal route would be \mbox{$A\to D\to F$}, with a commute time of 2. Conversely, if Alice stayed at work and Bob was driving home, his optimal route would be \mbox{$B\to D\to G$}, also with a commute time of 2. However, if both Alice and Bob were driving home at the same time there would be congestion at intersection $D$, and their combined travel time would be 6, not the intended 4. Thus, by optimising their routes independently of one another their competition for intersection $D$ would penalise both of them by 1. On the other hand, a global optimisation would show that a more optimal routing would be for Alice to take \mbox{$A\to C\to F$} (time 2.5), with Bob remaining on \mbox{$B\to D\to G$} (time 2). This would penalise Alice by only 0.5 for taking the longer road, but both Alice and Bob would no longer be penalised at the congested intersection, reducing their collective transit time to 4.5, a saving of 1.5. Note that Alice and Bob are not only better off collectively (i.e their joint travel time), but also individually. That is, Alice making the sacrifice of taking the longer route home actually benefits her individually, with an individual saving of 0.5. In this trivial example there is only one point of conflict in the network. In general, as the number of users scales up, the distinct ways in which combinations of conflicts could emerge grows exponentially.}\label{fig:traffic_opt}
\end{figure}

@@

\subsubsection{Least squares fitting}

A quantum-enhanced algorithm for performing least squares fitting\index{Least squares fitting} was described by \cite{HHL?}, potentially offering exponential enhancement, depending on the sparsity of the data.

@@

Despite all this optimism, there remains one major concern, one shared by any quantum algorithm offering only polynomial enhancement. In any real-world quantum computer fault-tolerance\index{Fault-tolerance} is necessarily required to enable the algorithm to be executed faithfully in the inevitable presence of noise. However, fault-tolerant codes necessarily induce a time and space overhead (i.e in terms of the number of physical qubits, and algorithmic runtime). If this overhead is too large it could well overpower the   enhancement offered by the underlying algorithm. For this reason, real-world implementations of these types of algorithms will require very careful consideration of the construction of their associated error correction circuitry, such that there is still some net tangible algorithmic gain at the end. The quadratic enhancement in algorithmic runtime is actually a bound based on the ideal-case where there are no errors. In a fault-tolerant construction the actual achievable enhancement will necessarily be less than this. Specifically, for a given runtime, if the enhancement in the searchable search space is a polynomial of order $p$, this equates to an effective increase in search tree depth by a factor of $p$.

>>>>

\begin{figure*}[!htb]
	\includegraphics[width=0.6\textwidth]{traffic_optimisation}
	\caption{Simple road network, where vertices represent intersections and edges represent roads. Edge weights indicate their associated travel time. The goal is for Alice and Bob to both drive home optimally, i.e minimising net commute time. Let us assume that the intersections do not delay single cars, but if they become congested (i.e more than one car simultaneously) they induce a time delay of 1 on all drivers present at the intersection. If Bob were to stay at work, and only Alice was attempting to drive home, her optimal route would be \mbox{$A\to D\to F$}, with a commute time of 2. Conversely, if Alice stayed at work and Bob was driving home, his optimal route would be \mbox{$B\to D\to G$}, also with a commute time of 2. However, if both Alice and Bob were driving home at the same time there would be congestion at intersection $D$, and their combined travel time would be 6, not the intended 4. Thus, by optimising their routes independently of one another their competition for intersection $D$ would penalise both of them by 1. On the other hand, a global optimisation would show that a more optimal routing would be for Alice to take \mbox{$A\to C\to F$} (time 2.5), with Bob remaining on \mbox{$B\to D\to G$} (time 2). This would penalise Alice by only 0.5 for taking the longer road, but both Alice and Bob would no longer be penalised at the congested intersection, reducing their collective transit time to 4.5, a saving of 1.5. Note that Alice and Bob are not only better off collectively (i.e their joint travel time), but also individually. That is, Alice making the sacrifice of taking the longer route home actually benefits her individually, with an individual saving of 0.5. In this trivial example there is only one point of conflict in the network. In general, as the number of users scales up, the distinct ways in which combinations of conflicts could emerge grows exponentially.}\label{fig:traffic_opt}
\end{figure*}

@@

\subsubsection{Curve fitting}\index{Curve fitting}

A quantum-enhanced algorithm for performing least squares curve fitting\index{Least squares fitting} was described by \cite{HHL?}, potentially offering exponential enhancement, depending on the sparsity of the data.

@@

Despite all this optimism, there remains one major concern, one shared by any quantum algorithm offering only polynomial enhancement. In any real-world quantum computer fault-tolerance\index{Fault-tolerance} is necessarily required to enable the algorithm to be executed faithfully in the inevitable presence of noise. However, fault-tolerant codes necessarily induce a time and space overhead (i.e in terms of the number of physical qubits, and algorithmic runtime). If this overhead is too large it could well overpower the   enhancement offered by the underlying algorithm. For this reason, real-world implementations of these types of algorithms will require very careful consideration of the construction of their associated error correction circuitry, such that there is still some net tangible algorithmic gain at the end. The quadratic enhancement in algorithmic runtime is actually a bound based on the ideal-case where there are no errors. In a fault-tolerant construction the actual achievable enhancement will necessarily be less than this. Specifically, for a given runtime, if the enhancement in the searchable search space is a polynomial of order $p$, this equates to an effective increase in search tree depth by a factor of $p$. For a useful quantum enhancement following fault-tolerance overhead, we obviously want \mbox{$p>1$}.

Note that for the quantum search method for enhancing \textbf{NP}-complete problems, a quadratic improvement is optimal. Therefore, \mbox{$p\leq 2$}.
